CommonMind Consortium: DLPFC

### 2020-10-12 combined_analysis/CTS/Glu.Rmd
consistant names

---
title: "CommonMind Consortium: DLPFC"
subtitle: "Cell type specific analysis of read count data by cohort"
author:
- name: "[Gabriel Hoffman](http://gabrielhoffman.github.io)$^{1}$ and Kelsey Montgomery$^{2}$"
  affiliation: | 
    [1] Icahn School of Medicine at Mount Sinai, New York
    [2] Sage Bionetworks, Seattle, WA
date: "Run on `r Sys.time()`"
documentclass: article
output:
  html_document:
    toc: true
    toc_float: true
params:
  upload: FALSE
  cellType: "GABA"
---

@@

rmarkdown::render("combined_analysis/CTS/GABA.Rmd")

@@

```{r knit2synapse, eval= FALSE}
library(synapser)
library(knit2synapse)
synLogin()
knit2synapse::createAndKnitToFolderEntity(file = "combined_analysis/combine_all_DLPFC_by_celltype.Rmd",
                                          parentId ="syn23241817",
                                          folderName = 'Analysis of read count data by cohort: GABA',
                                          overwrite=TRUE, 
                                          knitmd=TRUE)
```

@@

library(githubr)
parentId = 'syn23241817';
activityName = 'Analysis of read count data by cohort: GABA';
activityDescription = 'Analysis of read count data by cohort: GABA';

thisFileName <- 'GABA.Rmd'

>>>>

---
title: "CommonMind Consortium: DLPFC"
subtitle: "Cell type specific analysis of read count data by cohort"
author:
- name: "[Gabriel Hoffman](http://gabrielhoffman.github.io)$^{1}$ and Kelsey Montgomery$^{2}$"
  affiliation: | 
    [1] Icahn School of Medicine at Mount Sinai, New York
    [2] Sage Bionetworks, Seattle, WA
date: "Run on `r Sys.time()`"
documentclass: article
output:
  html_document:
    toc: true
    toc_float: true
params:
  upload: FALSE
  cellType: "Glu"
---

@@

rmarkdown::render("combined_analysis/CTS/Glu.Rmd")

@@

```{r knit2synapse, eval= FALSE}
library(synapser)
library(knit2synapse)
synLogin()
knit2synapse::createAndKnitToFolderEntity(file = "combined_analysis/combine_all_DLPFC_by_celltype.Rmd",
                                          parentId ="syn23241817",
                                          folderName = 'Analysis of read count data by cohort: Glu',
                                          overwrite=TRUE, 
                                          knitmd=TRUE)
```

@@

library(githubr)
parentId = 'syn23241817';
activityName = 'Analysis of read count data by cohort: Glu';
activityDescription = 'Analysis of read count data by cohort: Glu';

thisFileName <- 'Glu.Rmd'

### 2020-10-12 combined_analysis/CTS/MgAs.Rmd
consistant names

---
title: "CommonMind Consortium: DLPFC"
subtitle: "Cell type specific analysis of read count data by cohort"
author:
- name: "[Gabriel Hoffman](http://gabrielhoffman.github.io)$^{1}$ and Kelsey Montgomery$^{2}$"
  affiliation: | 
    [1] Icahn School of Medicine at Mount Sinai, New York
    [2] Sage Bionetworks, Seattle, WA
date: "Run on `r Sys.time()`"
documentclass: article
output:
  html_document:
    toc: true
    toc_float: true
params:
  upload: FALSE
  cellType: "GABA"
---

@@

rmarkdown::render("combined_analysis/combine_all_DLPFC_by_celltype.Rmd")

@@

```{r knit2synapse, eval= FALSE}
library(synapser)
library(knit2synapse)
synLogin()
knit2synapse::createAndKnitToFolderEntity(file = "combined_analysis/combine_all_DLPFC_by_celltype.Rmd",
                                          parentId ="syn22416298",
                                          folderName = 'Cell type specific analysis of read count data by cohort',
                                          overwrite=TRUE, 
                                          knitmd=TRUE)
```

@@

library(githubr)
parentId = 'syn22416298';
activityName = 'Cell type specific analysis of read count data by cohort';
activityDescription = 'Cell type specific analysis of read count data by cohort';

thisFileName <- 'combine_all_DLPFC_by_celltype.Rmd'

# Github link
thisRepo <- getRepo(repository = "CommonMindConsortium/covarr-de", ref="branch", refName='master')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('combined_analysis/',thisFileName))
```

@@

}) 
source("../common_functions/common_functions.R")   
# source("common_functions/common_functions.R")

@@

```{r store, eval=TRUE}
if( params$upload ){    
  # Code
  # Make sure these match the folder name and parent Id in the first chunk.
  CODE <- Folder(name = "Cell type specific analysis of read count data by cohort", parentId = "syn22416298")
  CODE <- synStore(CODE)

  # Store data 
  storeData = function( name, cellType, description){
    file = paste0(name, "_", cellType, ".RDS")
    saveRDS( eval(parse(text=name)), file=file)

    nEXP_OBJ = File(file, 
                    name = paste0(cellType, ' - ',description), 
                    parentId = CODE$properties$id)
    synStore(nEXP_OBJ, used = ALL_USED_IDs, executed = thisFile)
  }

>>>>

---
title: "CommonMind Consortium: DLPFC"
subtitle: "Cell type specific analysis of read count data by cohort"
author:
- name: "[Gabriel Hoffman](http://gabrielhoffman.github.io)$^{1}$ and Kelsey Montgomery$^{2}$"
  affiliation: | 
    [1] Icahn School of Medicine at Mount Sinai, New York
    [2] Sage Bionetworks, Seattle, WA
date: "Run on `r Sys.time()`"
documentclass: article
output:
  html_document:
    toc: true
    toc_float: true
params:
  upload: FALSE
  cellType: "MgAs"
---

@@

rmarkdown::render("combined_analysis/CTS/MgAs.Rmd")

@@

```{r knit2synapse, eval= FALSE}
library(synapser)
library(knit2synapse)
synLogin()
knit2synapse::createAndKnitToFolderEntity(file = "combined_analysis/combine_all_DLPFC_by_celltype.Rmd",
                                          parentId ="syn23241817",
                                          folderName = 'Analysis of read count data by cohort: MgAs',
                                          overwrite=TRUE, 
                                          knitmd=TRUE)
```

@@

library(githubr)
parentId = 'syn23241817';
activityName = 'Analysis of read count data by cohort: MgAs';
activityDescription = 'Analysis of read count data by cohort: MgAs';

thisFileName <- 'MgAs.Rmd'

# Github link
thisRepo <- getRepo(repository = "CommonMindConsortium/covarr-de", ref="branch", refName='master')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('combined_analysis/CTS/',thisFileName))
```

@@

}) 
source("../../common_functions/common_functions.R")   
# source("common_functions/common_functions.R")

@@

```{r store, eval=TRUE}
if( params$upload ){    
  # Code
  # Make sure these match the folder name and parent Id in the first chunk.
  CODE <- Folder(name = activityName, parentId = parentId)
  CODE <- synStore(CODE)

  # Store data 
  storeData = function( name, description){
    file = paste0(name, "_", params$cellType, ".RDS")
    saveRDS( eval(parse(text=name)), file=file)

    nEXP_OBJ = File(file, 
                    name = paste0(params$cellType, ' - ',description), 
                    parentId = CODE$properties$id)
    synStore(nEXP_OBJ, used = ALL_USED_IDs, executed = thisFile)
  }

### 2020-10-12 combined_analysis/CTS/Olig.Rmd
consistant names

---
title: "CommonMind Consortium: DLPFC"
subtitle: "Cell type specific analysis of read count data by cohort"
author:
- name: "[Gabriel Hoffman](http://gabrielhoffman.github.io)$^{1}$ and Kelsey Montgomery$^{2}$"
  affiliation: | 
    [1] Icahn School of Medicine at Mount Sinai, New York
    [2] Sage Bionetworks, Seattle, WA
date: "Run on `r Sys.time()`"
documentclass: article
output:
  html_document:
    toc: true
    toc_float: true
params:
  upload: FALSE
  cellType: "Glu"
---

@@

rmarkdown::render("combined_analysis/CTS/Glu.Rmd")

@@

```{r knit2synapse, eval= FALSE}
library(synapser)
library(knit2synapse)
synLogin()
knit2synapse::createAndKnitToFolderEntity(file = "combined_analysis/combine_all_DLPFC_by_celltype.Rmd",
                                          parentId ="syn23241817",
                                          folderName = 'Analysis of read count data by cohort: Glu',
                                          overwrite=TRUE, 
                                          knitmd=TRUE)
```

@@

library(githubr)
parentId = 'syn23241817';
activityName = 'Analysis of read count data by cohort: Glu';
activityDescription = 'Analysis of read count data by cohort: Glu';

thisFileName <- 'Glu.Rmd'

>>>>

---
title: "CommonMind Consortium: DLPFC"
subtitle: "Cell type specific analysis of read count data by cohort"
author:
- name: "[Gabriel Hoffman](http://gabrielhoffman.github.io)$^{1}$ and Kelsey Montgomery$^{2}$"
  affiliation: | 
    [1] Icahn School of Medicine at Mount Sinai, New York
    [2] Sage Bionetworks, Seattle, WA
date: "Run on `r Sys.time()`"
documentclass: article
output:
  html_document:
    toc: true
    toc_float: true
params:
  upload: FALSE
  cellType: "Olig"
---

@@

rmarkdown::render("combined_analysis/CTS/Olig.Rmd")

@@

```{r knit2synapse, eval= FALSE}
library(synapser)
library(knit2synapse)
synLogin()
knit2synapse::createAndKnitToFolderEntity(file = "combined_analysis/combine_all_DLPFC_by_celltype.Rmd",
                                          parentId ="syn23241817",
                                          folderName = 'Analysis of read count data by cohort: Olig',
                                          overwrite=TRUE, 
                                          knitmd=TRUE)
```

@@

library(githubr)
parentId = 'syn23241817';
activityName = 'Analysis of read count data by cohort: Olig';
activityDescription = 'Analysis of read count data by cohort: Olig';

thisFileName <- 'Olig.Rmd'
